### 2018-10-11 tex/abstract.tex
Version 1.2.

In large-scale data-parallel analytics, \textit{shuffle}, or the cross-network read and aggregation of partitioned data between tasks with data dependencies, usually brings in large network transfer overhead.
Due to the dependency constrains, execution of those descendant tasks could be delayed by logy shuffles.
To reduce shuffle overhead, we present \textit{SCache}, an open source \footnote{The URL is omitted due to double-blinded review requirements.} plug-in system that particularly focuses on shuffle optimization in frameworks defining jobs as \textit{directed acyclic graphs} (DAGs). 
By extracting and analyzing the DAGs and shuffle dependencies prior to the actual task execution, SCache can take full advantage of the system memory to accelerate the shuffle process. Meanwhile, it adopts heuristic-MinHeap scheduling combining with shuffle size prediction to pre-fetch shuffle data and balance the total size of data that will be processed by each descendant task on each node. 
{\color{red}
We have implemented SCache and customized Spark to use it as the external shuffle service and co-scheduler. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average.
}
{\color{blue}
We have implemented SCache as the external shuffle service and co-scheduler on both Apache Spark and Apache Hadoop. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average. On Apache Hadoop, Scache optimize end-to-end Terasort completion time by 15\%.
}
\end{abstract}

>>>>

In large-scale data-parallel analytics, \textit{shuffle}, or the cross-network read and aggregation of partitioned data between tasks with data dependencies, usually brings in large network transfer overhead.
Due to the dependency constrains, execution of those descendant tasks could be delayed by logy shuffles.
To reduce shuffle overhead, we present \textit{SCache}, an open source \footnote{The URL is omitted due to double-blinded review requirements.} plug-in system that particularly focuses on shuffle optimization in frameworks defining jobs as \textit{directed acyclic graphs} (DAGs). 
By extracting and analyzing the DAGs and shuffle dependencies prior to the actual task execution, SCache can take full advantage of the system memory to accelerate the shuffle process. Meanwhile, it adopts heuristic-MinHeap scheduling combining with shuffle size prediction to pre-fetch shuffle data and balance the total size of data that will be processed by each descendant task on each node. 
% {\color{red}
% We have implemented SCache and customized Spark to use it as the external shuffle service and co-scheduler. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
% Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average.
% }
{\color{blue}
We have implemented SCache as the external shuffle service and co-scheduler on both Apache Spark and Apache Hadoop. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster.
Those evaluations have demonstrated that, by incorporating SCache, the shuffle overhead of Spark can be reduced by nearly $89\%$, and the overall completion time of TPC-DS queries improves $40\%$ on average. On Apache Hadoop, Scache optimize end-to-end Terasort completion time by 15\%.
}
\end{abstract}

### 2018-10-11 tex/conclusion.tex
Version 1.2.

\section{Conclusion}
 In this paper, we present SCache, a cross-framework open source shuffle optimization system for DAG computing frameworks. SCache decouples the shuffle from computing pipeline and leverages shuffle data pre-fetching to mitigate the I/O overhead of the whole system. By scheduling tasks with application context, SCache bridges the gap among computing stages. 
 {\color{red}
 Our implementation with Spark and evaluations show that SCache can provide a promising speedup to the DAG framework. 
 }
 {\color{blue}
 At the expense of inserting hundred lines of code, we adapt Spark and Hadoop Mapreduce to SCache. Out evaluation result shows that SCache can provide a promising speedup to the DAG framework.
 }
 We believe that SCache is a simple and efficient system to enhance the performance of most DAG computing frameworks.

>>>>

\section{Conclusion}
 In this paper, we present SCache, a cross-framework open source shuffle optimization system for DAG computing frameworks. SCache decouples the shuffle from computing pipeline and leverages shuffle data pre-fetching to mitigate the I/O overhead of the whole system. By scheduling tasks with application context, SCache bridges the gap among computing stages. 
%  {\color{red}
%  Our implementation with Spark and evaluations show that SCache can provide a promising speedup to the DAG framework. 
%  }
 {\color{blue}
 At the expense of inserting hundred lines of code, we adapt Spark and Hadoop Mapreduce to SCache. Out evaluation result shows that SCache can provide a promising speedup to the DAG framework.
 }
 We believe that SCache is a simple and efficient system to enhance the performance of most DAG computing frameworks.

### 2018-10-11 tex/impl.tex
Version 1.2.

\section{Implementation}\label{impl}
This section presents an overview of the implementation of SCache -- an open source cross-framework shuffle data management system with a DAG co-scheduler. 
{\color{red}
Here we use Spark as an example of DAG framework to illustrate the work flow of shuffle optimization. 
We will first present the system overview in Subsection \ref{arch} while the following two subsections focus on the two constraints on memory management.
}
{\color{blue}
In Subsection \ref{arch}, we will first present the system overview, and then we will detail SCache memory management in Subsection \ref{memorymanage}. In Subsection \ref{crossframework}, we will evaluate cross-framework capability of SCache based on Hadoop Mapreduce and Spark. 
In the last Subsection \ref{fault}, we will introduce the current status of SCache fault tolerance.
}

\subsection{System Overview}\label{arch}
SCache consists of three components: a distributed shuffle data management system, a DAG co-scheduler, and a {\color{red}daemon inside Spark.} {\color{blue} worker daemon. As a plug-in system, SCache needs to rely on a DAG framework.} As shown in Figure \ref{fig:architecture}, SCache employs the legacy master-slaves architecture like GFS \cite{gfs} for shuffle data management system. 
The master node of SCache coordinates the shuffle blocks globally with application context. The worker node reserves memory to store blocks.
The coordination provides two guarantees: (a)data is stored in memory before tasks start and (b)data is scheduled on-off memory with all-or-nothing and context-aware constraints. 
The daemon bridges the communication between {\color{red}Spark} {\color{blue} DAG framework} and SCache. The co-scheduler is dedicated to pre-schedule reduce tasks with DAG information and enforce the scheduling results to {\color{red}Spark scheduler} {\color{blue} original scheduler in framework master}.

@@

{\color{red}
When a Spark job starts, the DAG will be first generated. 
During the DAG generation, the shuffle dependencies among Resilient Distributed Datasets (RDDs) will then be submitted through the daemon process in Spark driver. 
}
{\color{blue}
When a DAG job is submitted, the DAG information will be generated in framework master scheduler. 
Before the computing tasks begin, the shuffle dependecies are determined based on job configuration.
}
The SCache master recognizes all shuffle dependencies in a RPC call as a shuffle scheduling unit.
For each shuffle dependency, the shuffle ID, the type of partitioner, the number of map tasks, and the number of reduce tasks are included.  If there is a specialized partitioner, such as range partitioner, in the shuffle dependencies, the daemon will insert a sampling application before the dependent RDDs. We will elaborate the sampling procedure in the Section \ref{sampling}.

For the hash partitioner, when a map task finishes computing, the SCache daemon process will transfer the map output data from {\color{red}Spark executor's JVM }{\color{blue}framework worker} to the reserved memory through memory copy.
After that the slot will be released without blocking on disk operations.
When the shuffle map output is received, the SCache worker will notify the master of the block ID and reduce size distribution of this block (see map output in Figure \ref{fig:shuffle}).
If the collected map output data reach the observation threshold, the DAG co-scheduler will run the scheduling Algorithm \ref{hminheap} and \ref{mhminheap} to pre-schedule the reduce tasks and then broadcast the scheduling result to start pre-fetching on each worker.
More specifically, when a map task is finished, each node will receive a broadcast message. SCache worker will filter the reduce tasks ID that will be launched on itself and start pre-fetching shuffle data from the remote. 
{\color{red}
To enforce SCache pre-scheduled tasks -- node mapping, we insert some lines of codes in Spark DAG Scheduler.
For RDDs with shuffle dependencies, Spark DAG scheduler will consult SCache master to get the preferred location for each partition and set \textit{NODE\_LOCAL} locality level on corresponding reduce tasks.
}
{\color{blue}
In order to force DAG framework to run according to the SCache pre-scheduled results, we insert some lines of codes in framework scheduler.
After insertion, DAG scheduler will consult SCache master to get the preferred location for each partition and set \textit{NODE\_LOCAL} locality level on corresponding reduce tasks.
}

\subsubsection{Reservoir Sampling}\label{sampling}
If the submitted shuffle dependencies contain a range partitioner or a customized non-hash partitioner, the SCache master will send a sampling request to the {\color{red}daemon in Spark driver} {\color{blue}framework master}. 
The daemon then inserts a sampling job before the {\color{red}corresponding RDD} {\color{blue} submitted computing job}. 
The sampling job uses a reservoir sampling algorithm \cite{reservoir} on each partition {\color{red}of RDD}. 
For the sample number, we set the size to $3 \times number\ of\ partitions$ for balancing overhead and accuracy (it can be tuned by configuration). The sampling job randomly selects some items and performs a local shuffle with partitioner (see Figure \ref{fig:sample}). At the same time, the items number is counted as the weight. These sampling data will be aggregated by reduce ID on SCache master to predict the reduce partition size. After the prediction, SCache master will call Algorithm \ref{mhminheap} and \ref{hminheap} to do the scheduling.

@@

{\color{red}
\subsection{Cost of adapting DAG frameworks}
SCache provides API through RPC, such as \textit{putBlock(blockId)}, \textit{getBlock(blockId)}, and \textit{getScheduleResult(shuffleId)}. The concise design makes it easy to adapt DAG frameworks to enable SCache optimization. For example, it only takes about 500 lines of code in Spark to integrate SCache. By a glance of Hadoop source code, we believe that the costs of enabling SCache on MapReduce \cite{hadoop} and YARN \cite{yarn} based DAG computing framework, such as Tez \cite{tez}, are also very low.
}
{\color{blue}
\subsection{Analysis of cross-framework capability}\label{crossframework}
Shuffle optimization of SCache inevitably requires modification on dependent DAG framework. SCache provides API through RPC, such as \textit{putBlock(blockId)}, \textit{getBlock(blockId)}, and \textit{getScheduleResult(shuffleId)}. In order to use SCache, we mainly need to modify the two parts of the framework: (a)We need to insert codes in the DAG scheduler to let framework provide DAG information and follow the order. (b)The shuffle data between the Map task and the Reduce task should be transfer to SCahce Storge Management.

>>>>

\section{Implementation}\label{impl}
This section presents an overview of the implementation of SCache -- an open source cross-framework shuffle data management system with a DAG co-scheduler. 
% {\color{red}
% Here we use Spark as an example of DAG framework to illustrate the work flow of shuffle optimization. 
% We will first present the system overview in Subsection \ref{arch} while the following two subsections focus on the two constraints on memory management.
% }
{\color{blue}
In Subsection \ref{arch}, we will first present the system overview, and then we will detail SCache memory management in Subsection \ref{memorymanage}. In Subsection \ref{crossframework}, we will evaluate cross-framework capability of SCache based on Hadoop Mapreduce and Spark. 
In the last Subsection \ref{fault}, we will introduce the current status of SCache fault tolerance.
}

\subsection{System Overview}\label{arch}
SCache consists of three components: a distributed shuffle data management system, a DAG co-scheduler, and a %{\color{red}daemon inside Spark.}
{\color{blue} worker daemon. As a plug-in system, SCache needs to rely on a DAG framework.} As shown in Figure \ref{fig:architecture}, SCache employs the legacy master-slaves architecture like GFS \cite{gfs} for shuffle data management system. 
The master node of SCache coordinates the shuffle blocks globally with application context. The worker node reserves memory to store blocks.
The coordination provides two guarantees: (a)data is stored in memory before tasks start and (b)data is scheduled on-off memory with all-or-nothing and context-aware constraints. 
The daemon bridges the communication between %{\color{red}Spark}
{\color{blue} DAG framework} and SCache. The co-scheduler is dedicated to pre-schedule reduce tasks with DAG information and enforce the scheduling results to %{\color{red}Spark scheduler}
 {\color{blue} original scheduler in framework master}.

@@

% {\color{red}
% When a Spark job starts, the DAG will be first generated. 
% During the DAG generation, the shuffle dependencies among Resilient Distributed Datasets (RDDs) will then be submitted through the daemon process in Spark driver. 
% }
{\color{blue}
When a DAG job is submitted, the DAG information will be generated in framework master scheduler. 
Before the computing tasks begin, the shuffle dependecies are determined based on job configuration.
}
The SCache master recognizes all shuffle dependencies in a RPC call as a shuffle scheduling unit.
For each shuffle dependency, the shuffle ID, the type of partitioner, the number of map tasks, and the number of reduce tasks are included.  If there is a specialized partitioner, such as range partitioner, in the shuffle dependencies, the daemon will insert a sampling application before the dependent RDDs. We will elaborate the sampling procedure in the Section \ref{sampling}.

For the hash partitioner, when a map task finishes computing, the SCache daemon process will transfer the map output data from %{\color{red}Spark executor's JVM }
{\color{blue}framework worker} to the reserved memory through memory copy.
After that the slot will be released without blocking on disk operations.
When the shuffle map output is received, the SCache worker will notify the master of the block ID and reduce size distribution of this block (see map output in Figure \ref{fig:shuffle}).
If the collected map output data reach the observation threshold, the DAG co-scheduler will run the scheduling Algorithm \ref{hminheap} and \ref{mhminheap} to pre-schedule the reduce tasks and then broadcast the scheduling result to start pre-fetching on each worker.
More specifically, when a map task is finished, each node will receive a broadcast message. SCache worker will filter the reduce tasks ID that will be launched on itself and start pre-fetching shuffle data from the remote. 
% {\color{red}
% To enforce SCache pre-scheduled tasks -- node mapping, we insert some lines of codes in Spark DAG Scheduler.
% For RDDs with shuffle dependencies, Spark DAG scheduler will consult SCache master to get the preferred location for each partition and set \textit{NODE\_LOCAL} locality level on corresponding reduce tasks.
% }
{\color{blue}
In order to force DAG framework to run according to the SCache pre-scheduled results, we insert some lines of codes in framework scheduler.
After insertion, DAG scheduler will consult SCache master to get the preferred location for each partition and set \textit{NODE\_LOCAL} locality level on corresponding reduce tasks.
}

\subsubsection{Reservoir Sampling}\label{sampling}
If the submitted shuffle dependencies contain a range partitioner or a customized non-hash partitioner, the SCache master will send a sampling request to the %{\color{red}daemon in Spark driver} 
{\color{blue}framework master}. 
The daemon then inserts a sampling job before the %{\color{red}corresponding RDD}
{\color{blue} submitted computing job}. 
The sampling job uses a reservoir sampling algorithm \cite{reservoir} on each partition %{\color{red}of RDD}. 
For the sample number, we set the size to $3 \times number\ of\ partitions$ for balancing overhead and accuracy (it can be tuned by configuration). The sampling job randomly selects some items and performs a local shuffle with partitioner (see Figure \ref{fig:sample}). At the same time, the items number is counted as the weight. These sampling data will be aggregated by reduce ID on SCache master to predict the reduce partition size. After the prediction, SCache master will call Algorithm \ref{mhminheap} and \ref{hminheap} to do the scheduling.

@@

% {\color{red}
% \subsection{Cost of adapting DAG frameworks}
% SCache provides API through RPC, such as \textit{putBlock(blockId)}, \textit{getBlock(blockId)}, and \textit{getScheduleResult(shuffleId)}. The concise design makes it easy to adapt DAG frameworks to enable SCache optimization. For example, it only takes about 500 lines of code in Spark to integrate SCache. By a glance of Hadoop source code, we believe that the costs of enabling SCache on MapReduce \cite{hadoop} and YARN \cite{yarn} based DAG computing framework, such as Tez \cite{tez}, are also very low.
% }
{\color{blue}
\subsection{Analysis of cross-framework capability}\label{crossframework}
Shuffle optimization of SCache inevitably requires modification on dependent DAG framework. SCache provides API through RPC, such as \textit{putBlock(blockId)}, \textit{getBlock(blockId)}, and \textit{getScheduleResult(shuffleId)}. In order to use SCache, we mainly need to modify the two parts of the framework: (a)We need to insert codes in the DAG scheduler to let framework provide DAG information and follow the order. (b)The shuffle data between the Map task and the Reduce task should be transfer to SCahce Storge Management.

### 2018-10-11 tex/intro.tex
Version 1.2.

{\color{red}
We have implemented SCache and a customized Apache Spark \cite{apachespark}. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster. We conduct basic test GroupByTest. We also evaluate Terasort \cite{spark-tera} benchmark and standard workloads like TPC-DS \cite{tpcds} for multi-tenant modeling. In a nutshell, SCache can eliminate explicit shuffle process by at most $89\%$ in varied application scenarios. More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average.
}

>>>>

% {\color{red}
% We have implemented SCache and a customized Apache Spark \cite{apachespark}. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster. We conduct basic test GroupByTest. We also evaluate Terasort \cite{spark-tera} benchmark and standard workloads like TPC-DS \cite{tpcds} for multi-tenant modeling. In a nutshell, SCache can eliminate explicit shuffle process by at most $89\%$ in varied application scenarios. More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average.
% }
